---
title: "Predicting Astronauts Mission Duration using Tidymodels in R"
author: "Gaurav Sharma"
date: "17/07/2020"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE,
                      fig.width = 8,
                      fig.height = 5,
                      dpi = 180)
library(tidyverse)
library(tidymodels)
```

### Load the data
```{r}
ttload <- tidytuesdayR::tt_load(x = "2020-07-14")

astranauts <- ttload$astronauts

```
### Some EDA
Chang-Diaz, Franklin R. and Ross, Jerry L. have done the most number of missions in the history. Both have been to space 7 times. Both belong to US. 
Following table sows top 10 astronauts with most number of trips
```{r}
astranauts %>% 
    select(name, nationality, sex, hours_mission, total_hrs_sum) %>% 
    count(nationality, name, sex, sort = T) %>% 
    head(10) %>% 
    knitr::kable()
```

There are 40 countries that have been to space at least once. US tops the lists with 854 missions, Russia has 273 mission so far. 
Following table sows top 10 countries with most number of space missions.
```{r}
astranauts %>% 
    select(nationality) %>% 
    count(nationality, sort = T) %>% 
    head(10) %>% 
    knitr::kable()
```

```{r}

```

